Home

### 2023-05-05 index.Rmd
Added links

- Data comes from the Methods to Improve Diagnostic Assessment and Services (MIDAS) project – a longitudinal project that collects psychiatric patient data from outpatient and partial hospital settings.
- Patients at the partial hospital program attend multiple group therapies each day, as well as individual meeting with a therapist and psychiatrist. 
- Treatment is based in Acceptance and Commitment Therapy (ACT), an empirically-supported psychotherapy (Hayes et al., 2006).
---
The following visualizations are broken up into 4 sections:
1. [Sociodemographic and Treatment Characteristics]
2. [Diagnosis Visualizations]
3. [Treatment Progression Visualizations]
4. [Treatment Outcome Visualization]

>>>>

- Data comes from the Methods to Improve Diagnostic Assessment and Services (MIDAS) project – a longitudinal project that collects psychiatric patient data from outpatient and partial hospital settings.
- Patients at the partial hospital program attend multiple group therapies each day, as well as individual meeting with a therapist and psychiatrist. 
- Treatment is based in Acceptance and Commitment Therapy (ACT), an empirically-supported psychotherapy (Hayes et al., 2006).

#### The following visualizations are broken up into 4 sections:

1. [Sociodemographic and Treatment Characteristics](https://troy-hubert.github.io/Hospital_Visualizations/Data_Import.html)
2. [Diagnosis Visualizations](https://troy-hubert.github.io/Hospital_Visualizations/Diagnosis_Vis.html)
3. [Treatment Progression Visualizations](https://troy-hubert.github.io/Hospital_Visualizations/Anxiety_Vis.html)
4. [Treatment Outcome Visualization](https://troy-hubert.github.io/Hospital_Visualizations/Treatment_Outcomes.html)
